The ChEMBL database as Linked Open Data

### 2013-01-15 article.tex
reword the new discussion paragraph

The ongoing ChEMBL-RDF project is Open Source making it possible to others to convert ChEMBL to RDF too.
The ChEMBL team (JO, AG, MD) plans to be a primary source of a RDF version of ChEMBL, while others continue
exposing ChEMBL as RDF too (EW, PA). Various version may arise, exposing the data in different ontologies,
supporting community needs, though convergence may arise after a period of experimenting with ontologies that
will not survive the test of time. The availability of Open Source scripts ensure an easy switch from one
ontology to another.

>>>>

The ongoing ChEMBL-RDF project is Open Source making it possible to others to convert ChEMBL to RDF too.
The ChEMBL team (JO, AG, MD) plans to be a primary source of a RDF version of ChEMBL, while others continue
exposing ChEMBL as RDF (EW, PA). Different versions may arise which expose the data using different ontologies,
supporting current community needs, however, convergence is expected after a period of experimenting with ontologies that
are not practically useful. The availability of Open Source scripts ensures that the community can contribute to the
process of choosing a practically useful set of ontological terms.
